A Topic Model of Climate Change Literature

### 2019-07-12 methods.tex
submission

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}
\usepackage{standalone}
\usepackage[section]{placeins}
\usepackage{xr}
\externaldocument{main}

@@

		{\large{Draft current \@date}}

@@

\begin{document}
	% Title
	\title{A Topic Model of Climate Change Literature}
	\title{Words, words, words: Mapping the Matter of Climate Change Literature}
	\title{A Topography of Climate Change Research - Methods}
	\author[1,2]{Max Callaghan}
	\author[1,2]{Jan Minx}
	\author[2]{Piers M. Forster}

	\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
	\affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}

	\maketitle
	\begin{linenumbers}

@@

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science. We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}. Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report. This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods. Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to it's mitigation (for example on energy policy).

@@

	As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores. The combination of the two give the word scores in the document. For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.

@@

	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics. The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned. The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information. The spreadsheet shows each set of topics in adjacent columns. Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common. This helps authors to find an appropriate level of granularity for the analysis.

	\subsubsection*{Topic assignment to working groups}
	\label{topic-wg}
	A topic's score for each working group is calculated by summing the document-topic scores for all documents cited by that working group. We call the topic's primary working group that working group for which the above sum is the highest, but in some cases, where there are very few IPCC citations of documents related to a topic this can be misleading . For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic. Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III.

@@

	To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus.

@@

	\subsubsection*{Topic Map}
	The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's \textit{topic-ness} in a given topic. t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
		\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
		\label{top-rep-ks}
	\end{center}
\end{figure}

@@

%\bibliography{Mendeley}

\begin{thebibliography}{10}

	\bibitem{Grieneisen2011}
	Michael Grieneisen and Minghua Zhang.
	\newblock {The Current Status of Climate Change Research}.
	\newblock {\em Nature Climate Change}, 1:72--73, 2011.

	\bibitem{Minx2017l}
	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
	Edenhofer.
	\newblock {Learning about climate change solutions in the IPCC and beyond}.
	\newblock {\em Environmental Science {\&} Policy}, 2017.

	\bibitem{Le2014}
	Quoc~V. Le and Tomas Mikolov.
	\newblock {Distributed Representations of Sentences and Documents}.
	\newblock {\em ICML}, 32, 2014.

	\bibitem{Khabsa2014}
	Madian Khabsa and C~Lee Giles.
	\newblock {The number of scholarly documents on the public web}.
	\newblock {\em PLoS ONE}, 9(5), 2014.

	\bibitem{Lee1999}
	D~D Lee and H~S Seung.
	\newblock {Learning the parts of objects by non-negative matrix factorization.}
	\newblock {\em Nature}, 401(6755):788--791, 1999.

	\bibitem{Pedregosa2011}
	Fabian Pedregosa, Ga{\"{e}}l Varoquaux, Alexandre Gramfort, Vincent Michel,
	Bertrand Thirion, Olivier Grisel, Mathieu Blondel, Peter Prettenhofer, Ron
	Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre Passos, David Cournapeau,
	Matthieu Brucher, Mattheiu Perrot, and {\'{E}}douard Duchesnay.
	\newblock {Scikit-learn: Machine Learning in Python Fabian}.
	\newblock {\em Journal of Machine Learning Research}, 12:2825--2830, 2011.

	\bibitem{Chaney2012}
	Allison J~B Chaney and David~M. Blei.
	\newblock {Visualizing Topic Models}.
	\newblock {\em Icwsm}, pages 419--422, 2012.

	\bibitem{Hall2008}
	David Hall, Daniel Jurafsky, and Christopher~D. Manning.
	\newblock {Studying the history of ideas using topic models}.
	\newblock {\em Proceedings of the Conference on Empirical Methods in Natural
		Language Processing - EMNLP '08}, pages 363--371, 2008.

	\bibitem{vandermaaten2008}
	Laurens van~der Maaten and Geoffrey Hinton.
	\newblock {Visualizing Data using t-SNE}.
	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.

	\bibitem{Meehl2007}
	Gerald~A. Meehl, Curt Covey, Thomas Delworth, Mojib Latif, Bryant McAvaney,
	John~F.B. Mitchell, Ronald~J. Stouffer, and Karl~E. Taylor.
	\newblock {The WCRP CMIP3 multimodel dataset: A new era in climatic change
		research}.
	\newblock {\em Bulletin of the American Meteorological Society},
	88(9):1383--1394, 2007.

\end{thebibliography}

>>>>

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}
\usepackage{standalone}
\usepackage[section]{placeins}

\usepackage{xr}
\externaldocument{main}

@@

		{\large{ \@date}}

@@

\begin{document}
	% Title
	\title{A Topic Model of Climate Change Literature}
	\title{Words, words, words: Mapping the Matter of Climate Change Literature}
	\title{A Topography of Climate Change Research}

\author[1,2]{Max Callaghan*}
\author[1,2]{Jan Minx}
\author[2]{Piers M. Forster}

\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}
	\maketitle
	\begin{linenumbers}

		\section*{Methods}

					\setcounter{table}{0}
		\renewcommand\thetable{SI.\arabic{table}}

@@

		We also tested the query documented in \cite{Haunschild2016}, by checking a random sample of documents exclusive to it. We found that the majority of additional documents were not relevant, and decided to use only the query from \cite{Grieneisen2011}.

		We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science. We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}. Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report. This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods. Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to its mitigation (for example on energy policy).

@@

		As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores. The combination of the two approach the word scores in the document. For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.

@@

		Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics. The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned. The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information. The spreadsheet shows each set of topics in adjacent columns. Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common. This helps authors to find an appropriate level of granularity for the analysis. Statistical methods for the selection of topic model parameters are available but they do not necessarily align with human perceptions of topic model quality \cite{Chang2009}. We make a judgement based on subjective criteria, but for transparency publish the results of the analysis for different numbers of topics in figure \ref{top-rep-ks}. The main conclusions drawn about the rapid growth and under-representation of solutions-relevant topics are stable across models.

		\subsubsection*{Topic assignment to working groups}
		\label{topic-wg}
		A topic's score for each working group is calculated by summing the document-topic scores for all documents cited by that working group. We call the topic's primary working group that working group for which the above sum is the highest, but in some cases, where there are very few IPCC citations of documents related to a topic this can be misleading . For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic. Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III. We point out that topics are in any case mixtures of documents cited by different working groups, and stress that the colouring of the topics by working group is merely illustrative.

@@

		To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus (excluding documents published after the last assessment report). Disciplinary representation is calculated in the same way.

@@

		It is an indication of the diversity of disciplines within the set of documents related to a topic.

		\subsubsection*{Topic Map}
		The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's \textit{topic-ness} in a given topic. t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}. Documents are placed on the map such that documents with similar combinations of topics are close together.

@@

	\section*{Supplementary Files}

	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map

	\medskip\noindent
	\texttt{topics.csv} Contains a list of the topics, along with their features discussed in this paper. The top 10 words associated with each topic are also shown

\medskip\noindent
	\texttt{doctopics.csv} Contains a list of document-topic scores, which can be cross-referenced with the document and topic ids in \texttt{docs.csv} and \texttt{topics.csv}.

	\section*{Supplementary Figures}

	\begin{figure}
		\begin{center}
			\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
			\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
			\label{top-rep-ks}
		\end{center}
	\end{figure}
	\bibliography{Mendeley}
